Comparing Results with Mafessoni et al.

### 2019-07-10 PlottingScripts/ProcessedData/ScoopCheck.Rmd
saving r scripts

p_comp <- 
  ggplot(to_plot, 
         aes(x=Adjusted_Log10p, 
             y= -log10(pvalue_glm_filt), 
             color = strict_mask)) +
  geom_point(shape = 1,
             size = 1,
             alpha = 0.3) +
  labs(x = 'Q-association',
       y = 'LD-association') +
  scale_color_grey(start = 0.1, end = 0.6) +
  guides(color = F) +
  facet_wrap(.~strict_mask)+
  theme_classic() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 20))

@@

ggsave(paste0(figurePath,
              'Mafessoni_MutSpect.jpg'),
       m_plot, 
       height = 12,
       width = 10)

>>>>

p_comp <- 
  ggplot(to_plot, 
         aes(x=Adjusted_Log10p, 
             y= -log10(pvalue_glm_filt), 
             color = strict_mask)) +
  geom_point(shape = 1,
             size = 1,
             alpha = 0.3) +
  labs(x = '-log10(p) Q-association',
       y = '-log10(p) LD-association') +
  scale_color_grey(start = 0.1, end = 0.6) +
  guides(color = F) +
  facet_wrap(.~strict_mask)+
  theme_classic() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 20))

@@

ggsave(paste0(figurePath,
              'Mafessoni_MutSpect.jpg'),
       m_plot, 
       height = 10,
       width = 10)
